landlord

### 2022-12-06 src/landlord.Rmd
changed landlord score calc 80: eviction notice, 20: security deposit, no entry notice

select_MSAs <- read_sheet("https://docs.google.com/spreadsheets/d/1lmTpSDwVANxdAg5sW87Q8l_gtig7M0EjPPJ6J5_7dwg/edit?usp=sharing")
```

```{r}
#filter by new MSA list
new_MSA_list <- unique(select_MSAs$cbsa)

MSA_landlord_data <- MSA_landlord_data %>% 
  filter(cbsa %in% c(new_MSA_list))
```

@@

#notice_of_entry_days
MSA_landlord_data <- MSA_landlord_data %>% 
  mutate(
    notice_for_entry_days_num = case_when(
      notice_for_entry_days == "N" ~ 1.0, 
      notice_for_entry_days == "0" ~ 1.0,
      notice_for_entry_days == "0.5" ~ 0.75,
      notice_for_entry_days == "1" ~ 0.5,
      notice_for_entry_days == "2" ~ 0.0,))
```

@@

#Weights must sum to 1
landlord_weights <- c(0.9, 0.05, 0.05)

#make landlord_score column
MSA_landlord_data <- MSA_landlord_data %>% 
  mutate(
    landlord_score = MSA #this is just a place holder
  )
size <- dim(MSA_landlord_data)
for (i in 1:size[1]) {
  MSA_x_data <- c(MSA_landlord_data$eviction_notice_days_normalized_inverted[i],
                  MSA_landlord_data$security_depopsit_limit_num[i],
                  MSA_landlord_data$notice_for_entry_days_num[i]
                  )
  MSA_landlord_data$landlord_score[i] = weighted.mean(MSA_x_data, landlord_weights)
}
```

@@

>>>>

# select_MSAs <- read_sheet("https://docs.google.com/spreadsheets/d/1lmTpSDwVANxdAg5sW87Q8l_gtig7M0EjPPJ6J5_7dwg/edit?usp=sharing")
```

```{r}
#filter by new MSA list
# new_MSA_list <- unique(select_MSAs$cbsa)
# 
# MSA_landlord_data <- MSA_landlord_data %>% 
#   filter(cbsa %in% c(new_MSA_list))
```

@@

# #notice_of_entry_days
# MSA_landlord_data <- MSA_landlord_data %>% 
#   mutate(
#     notice_for_entry_days_num = case_when(
#       notice_for_entry_days == "N" ~ 1.0, 
#       notice_for_entry_days == "0" ~ 1.0,
#       notice_for_entry_days == "0.5" ~ 0.75,
#       notice_for_entry_days == "1" ~ 0.5,
#       notice_for_entry_days == "2" ~ 0.0,))
```

@@

#Weights must sum to 1
landlord_weights <- c(0.8, 0.2)

#make landlord_score column
MSA_landlord_data <- MSA_landlord_data %>% 
  mutate(
    landlord_score = MSA #this is just a place holder
  )
size <- dim(MSA_landlord_data)
for (i in 1:size[1]) {
  MSA_x_data <- c(MSA_landlord_data$eviction_notice_days_normalized_inverted[i],
                  MSA_landlord_data$security_depopsit_limit_num[i]
                  )
  MSA_landlord_data$landlord_score[i] = weighted.mean(MSA_x_data, landlord_weights)
}
```

@@

```{r}
#write result to google sheet
gs4_create("MSA_landlord_score")
sheet_write(MSA_landlord_data, ss = "https://docs.google.com/spreadsheets/d/1nLpDhM88a3rEBDVK5RZlk2B6QuwVIwvsfE5HeBz0mLo/edit?usp=sharing", sheet = "MSA_landlord_data")
```
